Learning Network Size while Training with ShrinkNets

### 2018-02-09 paper/ICML/approach.tex

\subsubsection{Neuron killing}
\textbf{Threshold strategy} \\ We kill neurons based on a threshold (in absolute
value), this is the method used by deep compression. It is bad because it is
scale dependant and is not robust to noise in the gradients (explain that)
\textbf{Sign change strategy} \\ We look at when the sign change. This is also
sensitive to noise but has the advantage
\textbf{Sign variance strategy}

>>>>

\subsubsection{Neuron killing}
\textbf{Threshold strategy}:  We kill neurons based on a threshold (in absolute
value), this is the method used by deep compression. It is bad because it is
scale dependant and is not robust to noise in the gradients (explain that)
\\ \textbf{Sign change strategy}:  We look at when the sign change. This is also
sensitive to noise but has the advantage
\textbf{Sign variance strategy}: We measure the variance of the sign ($-1, 1$) of each component in the \textit{Switch Layer}, and consider it dead when it goes over a predefined threshold. \gl{Maybe we should add some intuition on why it makes sense}. \gl{We should probably explain the impact of $\gamma$ and report numbers from the expertiment that show that it does not hurt too much to kill neurons, we have the data in this experiment in the evaluation that we probably want to remove later.}

### 2018-02-09 paper/ICML/theory.tex

\section{Theoretical analysis}

\subsection{Notations}

\par In order to avoid any potential ambiguity, in this section we will
describe in details the mathematical notations used in this article. Non-bold
letters represent scalar values, while bold lowercase and upper case
repectively denote vectors and matrices. $\bm{A}^T$ stands for the transpose of
the matrix $\bm{A}$. Subscripts are used to index particular elements of
vectors and matrices. $\bm{x}_i$, $\bm{A}_i$, $\left(\bm{A}^T\right)_j$ and
$\bm{A}_{i,j}$ respectively correspond to the $i^{th}$ component of $\bm{x}$,
the $i^{th}$ row of $\bm{A}$, the $j^{th}$ column of $\bm{A}$ and the $j^{th}$
component of the $i^{th}$ row of $\bm{A}$. All the following definitions assume
$\bm{A}$ to be an $n\times p$ matrix.  For any vetor $\bm{b}$ with $n$
components, we define $\diag{\bm{b}}$ a $n\times n$ matrix such that: $\forall
1 \leq i \leq n$, $\diag{\bm{b}}_{i, i} = \bm{b}_i$ and $0$ otherwise.  For any $l \in \left[0, +\infty\right]$ we define the norm: $\norm{\bm{A}}_l =
\left(\sum_{i=1}^n \sum_{j=1}^p \abs{\bm{A}_{i, j}}^l\right)^{\frac{1}{p}}$. For the rest of this paper and unless stated otherwise, $\bm{y}$ will represent the output of a network, $\bm{x}$ the input, $\bm{b}$ a bias, $\lambda$ regularization factors, $\Omega$ regularization methods, $\bm{\theta}$ general model parameters and $a$ will stand for any element-wise activation function. The only constraint that we want to enforce is that $a(0) = 0$. We use $\intint{u, v}$ to denote inteveral of integers, $\bm{0}$ is the null vector (size depending on the context). $\#S$ is meant to represent the cardinality of a set $S$. To simplify the notation of function composition we use the following operator: $g(f(\bm{x})) = (f \circ g)(\bm{x})$ and for a long sequence of functions from $f_1$ to $f_n$ we use: $f_n(...f_1(\bm{x})) = \left(\bigcirc_{k = 1}^n f_k\right)(\bm{x})$.
\subsection{Definition}

\begin{equation}
  \Omega_\lambda^s = \lambda \norm{\bm{\beta}}_1
\end{equation}

@@

Because $\forall i, \#\bm{\theta}_i = n$, To make the notation simpler,
we now embed $\sqrt{n}$ inside $\lambda$.

Since group sparsity and ShrinkNets try to achieve the same goal we will try to understand their similarities and differences. First let's recall the two problems. The ShrinkNet problem is:

\begin{equation}
  \min_{\bm{A}, \bm{\beta}} \norm{\bm{y} - \bm{A}\diag{\bm{\beta}}\bm{x}}_2^2 + \Omega_\lambda^s
\end{equation}

@@

has many global minimum (\cref{shrinknet_regularized_minimum}) for all $p>0$. This is the reason we define the \textit{regularized ShrinkNet penalty}:

>>>>

\subsection{Relation to Group Sparsity}

% \begin{equation}
%   \Omega_\lambda^s = \lambda \norm{\bm{\beta}}_1
% \end{equation}

@@

Because $\forall i, \#\bm{\theta}_i = n$, To make the notation simpler,
we embedded $\sqrt{n}$ inside $\lambda$.

Since group sparsity and ShrinkNets try to achieve the same goal we will try to understand their similarities and differences. First let's recall the two problems. The original ShrinkNet problem is:

\begin{equation}
  \min_{\bm{A}, \bm{\beta}} \norm{\bm{y} - \bm{A}\diag{\bm{\beta}}\bm{x}}_2^2 + \lambda \norm{\bm{\beta}}_1
\end{equation}

@@

has many global minimum (\cref{shrinknet_regularized_minimum}) for all $p>0$. This is the reason we defined the \textit{regularized ShrinkNet penalty} earlier this way:
